\subsection{}



\subsubsection*{Representable functors preserve monomorphisms}

There exists by assumption an object~$c$ of~$\cat{C}$ for which the two functors~$F$ and~$\cat{C}(c, \ph)$ are isomorphic.
Let~$α$ be a natural isomorphism from~$\cat{C}(c, \ph)$ to~$F$.

Let~$f \colon x \to y$ be a monomorphism in~$\cat{C}$.
This entails that the induced map~$f_* \colon \cat{C}(c, x) \to \cat{C}(c, y)$ is injective.
We thus have the commutative square diagram
\[
	\begin{tikzcd}
		\cat{C}(c, x)
		\arrow{r}[above]{f_*}
		\arrow{d}[left]{α_x}
		&
		\cat{C}(c, y)
		\arrow{d}[right]{α_y}
		\\
		F(x)
		\arrow{r}[above]{F(f)}
		&
		F(y)
	\end{tikzcd}
\]
in which both vertical arrows are bijections and the upper horizontal arrow is injective.
It follows that
\[
	F(f) = α_y f_* α_x^{-1}
\]
is a composite of injections, and therefore itself injective.
This shows that the functor~$F$ preserves monomorphisms, as the monomorphisms in~$\Set$ are precisely those maps that are injective.



\subsubsection*{A non-representable functor}

For every group~$G$ let~$C(G)$ be its set of conjugacy classes.
Every homomorphism of groups~$φ \colon G \to H$ induces a map~$C φ \colon C(G) \to C(H)$ that assigns to the conjugacy class of an element~$g$ the conjugacy class of the image element~$φ(g)$.
The assignment~$C$ is a functor from~$\Group$ to~$\Set$.

Let~$\symm_3$ be the symmetric group on three letters.
This group contains two elements~$ρ_1$ and~$ρ_2$ of order~$3$, which are conjugated to one another.
The two elements~$ρ_1$ and~$ρ_2$ are related via~$ρ_2 = ρ_1^2$.

Let~$i$ be the inclusion homomorphism from~$ℤ / 3$ to~$\symm_3$ given by~$i(\class{1}) = ρ_1$.
Then also
\[
	i(\class{2})
	=
	i(2 ⋅ \class{1})
	=
	i(\class{1})^2
	=
	ρ_1^2
	=
	ρ_2 \,.
\]
The group~$ℤ / 3$ is abelian, whence each element of~$ℤ / 3$ forms its own conjugacy class.
The homomorphism~$i$ therefore maps the two non-conjugated elements~$\class{1}$ and~$\class{2}$ of~$ℤ / 3$ onto the two conjugated elements~$ρ_1$ and~$ρ_2$ of~$\symm_3$.
This tells us that the induced map~$C i$ is not injective.

We find that the functor~$C$ does not preserve monomorphisms.
It therefore cannot be representable.
