\subsection*{Equivalences between skeletal categories are isomorphisms}

For every category~$\cat{C}$ let~$\Iso(\cat{C})$ be the class of isomorphism classes of objects of~$\cat{C}$.
We note that every functor~$F \colon \cat{C} \to \cat{D}$ induces a function~$\Iso(F)$ from~$\Iso(\cat{C})$ to~$\Iso(\cat{D})$ via~$\class{c} \mapsto \class{F c}$.
The construction~$\Iso$ is functorial.

\begin{lemma}
	\label{isomorphic functors induce the same map on iso classes}
	Let~$F, G \colon \cat{C} \to \cat{D}$ be two parallel functors.
	If~$F$ and~$G$ are isomorphic, then the induced maps~$\Iso(F)$ and~$\Iso(G)$ are equal.
\end{lemma}

\begin{proof}
	We have for every object~$c$ of~$\cat{C}$ the isomorphism~$F c ≅ G c$ and therefore the equality
	\[
		\Iso(F)(c)
		=
		\class{F c}
		=
		\class{G c}
		=
		\Iso(G)(c) \,.
	\]
	This shows that~$\Iso(F) = \Iso(G)$.
\end{proof}

\begin{proposition}
	\label{equivalence induces bijection between iso classes}
	Let~$F \colon \cat{C} \to \cat{D}$ be an equivalence of categories with quasi-inverse~$G \colon \cat{D} \to \cat{C}$.
	The induced map~$\Iso(F)$ is bijective with inverse~$\Iso(G)$.
\end{proposition}

\begin{proof}
	There exists an isomorphism of functors between~$G F$ and~$\Id_{\cat{C}}$.
	It follows from \cref{isomorphic functors induce the same map on iso classes} that
	\[
		\Iso(G) \Iso(F)
		=
		\Iso(G F)
		=
		\Iso( \Id_{\cat{C}} )
		=
		\Id_{\Iso(\cat{C})} \,.
	\]
	We find in the same way that also~$\Iso(F) \Iso(G) = \Id_{\Iso(\cat{D})}$.
\end{proof}

\begin{proposition}
	\label{full faithful and bijective is isomorphism}
	Let~$F$ be a functor that is full, faithful, and induces a bijection between objects.
	Then~$F$ is an isomorphism.
	\qed
\end{proposition}

\begin{proof}
	It follows that~$F$ also induces a bijection on morphisms.
\end{proof}

\begin{corollary}
	An equivalence between skeletal categories is already an isomorphism of categories.
\end{corollary}

\begin{proof}
	Let~$F \colon \cat{C} \to \cat{D}$ be an equivalence between skeletal categories.
	It follows from \cref{equivalence induces bijection between iso classes} and~$\cat{C}$ and~$\cat{D}$ being skeletal that~$F$ induces a bijection between objects.
	The functor~$F$ is also full and faithful.
	It is therefore an isomorphism of categories by \cref{full faithful and bijective is isomorphism}.
\end{proof}
