\subsection{}



\subsubsection{}

We show the following result:

\begin{proposition}
	\label{composite of faithful full essentially surjective}
	Let~$F \colon \cat{C} \to \cat{D}$ and~$G \colon \cat{D} \to \cat{E}$ be two functors.
	\begin{enumerate}

		\item
			If both~$F$ and~$G$ are faithful, then their composite~$G F$ is again faithful.

		\item
			If both~$F$ and~$G$ are full, then their composite~$G F$ is again full.

		\item
			If both~$F$ and~$G$ are essentially surjective, then their composite~$G F$ is again essentially surjective.

	\end{enumerate}
\end{proposition}


\begin{proof}
	We observe for every two objects~$x$ and~$y$ in~$\cat{C}$ the following commutative diagram of sets and functions between these sets:
	\[
		\begin{tikzcd}[column sep = small]
			\cat{C}(x, y)
			\arrow{rr}[above]{GF}
			\arrow{dr}[below left]{F}
			&
			{}
			&
			\cat{E}(GF x, GF y)
			\\
			{}
			&
			\cat{D}(F x, F y)
			\arrow{ur}[below right]{G}
			&
			{}
		\end{tikzcd}
	\]
	\begin{enumerate}

		\item
			Let~$x$ and~$y$ be any two objects of~$\cat{C}$.
			The maps~$F \colon \cat{C}(x, y) \to \cat{D}(F x, F y)$ and~$G \colon \cat{D}(F x, F y) \to \cat{E}(GF x, GF y)$ are both injective, whence their composite~$GF \colon \cat{C}(x, y) \to \cat{E}(GF x, GF y)$ is again injective.

		\item
			Let~$x$ and~$y$ be any two objects of~$\cat{C}$.
			The maps~$F \colon \cat{C}(x, y) \to \cat{D}(F x, F y)$ and~$G \colon \cat{D}(F x, F y) \to \cat{E}(GF x, GF y)$ are both surjective, whence their composite~$GF \colon \cat{C}(x, y) \to \cat{E}(GF x, GF y)$ is again surjective.

		\item
			For every category~$\cat{X}$ we denote by~$\Iso(\cat{X})$ the collection of isomorphisms classes of objects of~$\cat{X}$.
			Functors preserve isomorphisms, whence every functor~$H \colon \cat{X} \to \cat{Y}$ induces a function~$\Iso(H) \colon \Iso(\cat{X}) \to \Iso(\cat{Y})$ given by~$\Iso(H)(\class{x}) = \class{H x}$.

			In the given situation we have the following commutative diagram:
			\[
				\begin{tikzcd}[column sep = normal]
					\Iso(\cat{C})
					\arrow{rr}[above]{\Iso(GF)}
					\arrow{dr}[below left]{\Iso(F)}
					&
					{}
					&
					\Iso(\cat{E})
					\\
					{}
					&
					\Iso(\cat{D})
					\arrow{ur}[below right]{\Iso(G)}
					&
					{}
				\end{tikzcd}
			\]
			The functions~$\Iso(F)$ and~$\Iso(G)$ are both surjective by assumption.
			Their composite~$\Iso(G) ∘ \Iso(F) = \Iso(GF)$ is therefore again surjective.
		\qedhere

	\end{enumerate}
\end{proof}



\subsubsection{}

According to Theorem~1.5.9 there exist functors~$F \colon \cat{C} \to \cat{D}$ and~$G \colon \cat{D} \to \cat{E}$ both of which are full, faithful, and essentially surjective.
It follows from \cref{composite of faithful full essentially surjective} that their composite~$G F \colon \cat{C} \to \cat{E}$ is again full, faithful, and essentially surjective.
Once again according to Theorem~1.5.9, this means that~$\cat{C}$ and~$\cat{E}$ are equivalent.

We have thus proven that equivalence of categories is transitive.

Every category is equivalent to itself via its identity functor.
Equivalence of categories is therefore reflexive.

Two categories~$\cat{C}$ and~$\cat{D}$ are equivalent if and only if there exist functors~$F \colon \cat{C} \to \cat{D}$ and~$G \colon \cat{D} \to \cat{C}$ with~$GF ≅ \Id_{\cat{C}}$ and~$FG ≅ \Id_{\cat{D}}$.
This formulation is symmetric in~$\cat{C}$ and~$\cat{D}$, whence equivalence of categories is symmetric.
